Template for indicator documentation

### 2023-09-14 slitasje.Rmd
bug: fix crossrefs

7.  Define [homogeneous impact areas](#HIA) (HIA)

@@

We also have a separate [summary file](##exp-natureType-summary) where
the nature types are manually mapped the NiN variables and to the correct NiN-main types. We can use this to find the nature types associated with the NiN main types
that we are interested in.

@@

### Homogeneous impact areas {#HIA}

I want to use the [Homogeneous Impact Areas](#HIA) (HIA) to define
smaller regions into which I can extrapolate the indicator values. This
data is generated by discretizing the Norwegian Infrastructure Index. I
refer to the ordinal values of the four HIA classes as their *Human
Impact Factor* (HIF). This is just to keep the approach separate from
the Norwegian Infrastructure Index.

>>>>

7.  Define [homogeneous impact areas](#HIA-slitasje) (HIA)

@@

We also have a separate [summary file](#exp-natureType-summary) where
the nature types are manually mapped to the correct NiN-main typesand to the NiN variables  that are recorded in each nature type. We can use this to find the nature types associated with the NiN main types
that we are interested in.

@@

### Homogeneous impact areas {#HIA-slitasje}

I want to use the [Homogeneous Impact Areas](#homogeneous-impact-areas) (HIA) to define
smaller regions into which I can extrapolate the indicator values. This
data is generated by discretizing the Norwegian Infrastructure Index. I
refer to the ordinal values of the four HIA classes as their *Human
Impact Factor* (HIF). This is just to keep the approach separate from
the Norwegian Infrastructure Index.
